The Feasibility of Stylometry as a Service

### 2013-12-07 paper/paper.tex
Added section outline
Started to add paragraph on anonymouth architecture.

>>>>

\section{Design}

\subsection{Anonymouth Architecture Review}

The architecture of Anonymouth is that of a conventional desktop
application.  It uses a layered architecture with essentially two main
components: the frontend Graphical User Interface (GUI) and the
backend, consisting of the Weka machine learning toolkit and Jstylo.
Jystlo is PSAL's stylometric analysis software.   Since Anonymouth was
designed as a monolithic application, there are direct dependencies
between the layers without the use of an adaptation layer.

\section{Security Analysis}

\section{Privacy Analysis}

\section{Implementation Details}

\section{Comparison to Stand-alone Application}

\section{Evaluation}

\section{Conclusion}

\section{Proposal stuff --- will be removed}
